Introduction to Olavo de Carvalho´s Work

### 2017-11-04 texts/philosophy/introolavo.tex
matlab algebra linear for invert matrix using GaussJordan

	Um método é um conjunto de proposições auto-evidentes (ou provadas com base nelas) que delimitam um objeto e os meios de conhecê-lo.
	O bom método não define o seu objeto, mas recebe essa definição de uma prévia descrição fenomenológica.
	\section{Philosopher Maturity}
	\subsection{Impression of Reality}
	\subsubsection{Senses}
	\subsubsection{Limited Structure of the Reality}
	\subsection{Unification}
	\subsubsection{Reality Unification}
	\subsubsection{Conscience Unification}
	\subsubsection{12 layers of personality}

>>>>

	Um método é um conjunto de proposições auto-evidentes (ou provadas com base nelas) que delimitam um objeto e os meios de conhecê-lo.
	O bom método não define o seu objeto, mas recebe essa definição de uma prévia descrição fenomenológica.
	\section{Philosopher Maturity}
	\subsection{Impression of Reality}
	\subsubsection{Senses}
	\subsubsection{Limited Structure of the Reality}
	Kantism is not a philosophy. It`s a practical joke.
	Kant had to be VERY stupid to not understand that our apprehending only the phenomenic appearances, and not the thing in itself, is not a limitation in us, but of the things in themselves. If he had noticed this, he would have realized that his theory DOES NOT MEAN ANYTHING.
	All modern science is based on a phenomenist metaphysics, in which there are no real beings, just measurable appearances. It is so because no real entity is exhausted on which a science, or all of them together, can say about it. Besides, each one only asks questions about the object that pertain to its own methodology and not about the ontological structure of the object itself. This structure remains outside the reach of each science in particular and cannot be reengineered by the mere articulation of a number of the sciences. The experience of REALITY is an anterior necessity for the possibility of any science, which they just complement with specific details. This same experience of reality remains outside of epistemological control of any science.
	No scientific explanation refers to the fact in itself, as small as it may be, and even less accounts for its causes. It just highlights the aspects of the fact that correspond to the methodological perspective of that science in particular. "Reality" is entirely out of all that. Ninety-nine point ninety-nine percent of science professionals ignore that this is how things are.
	Practicing any science without the constant critical examination of its epistemological pillars, and therefore of its own limitations, causes a state of hypnotic hallucination. In such a state the person denies the validity of his spontaneous perception of things - which is the foundation of any science - and substitutes it for some hypothetical system that gives him the impression of being scientific. Many scientists end up becoming like Felix, the Cat ( https://www.youtube.com/watch?v=amGbBFsiuzc ), living in a world drawn by themselves.
	When a science professor says there is no significant genetic differences between a monkey and a three-year-old, he imagines that this difference really does not exist, and not that it is his genetic perspective that is insufficient to apprehend it.
	Ultimately, the sciences as they exist today are not meant to know the world, but to fabricate it as an industrialized product.
	Olavo de Carvalho
	\subsection{Unification}
	\subsubsection{Reality Unification}
	\subsubsection{Conscience Unification}
	\subsubsection{12 layers of personality}
